gammSlice 用法

### 2019-03-11 gammSlice.Rmd
修改{1}为{l}

$$\begin{array}{1}
y_{ij}|x_{ij},\beta_0,\beta_x,U_i,\mathop \to \limits ^{ind} Bernoulli(logit^{-1}(\beta_0+\beta_xx_{ij}+U_i)),\quad 1\leq i \leq m,1\leq j \leq n \\
x_{ij}\mathop \to \limits ^{ind}Uniform(0,1),\quad U_i|\sigma^2 \mathop \to \limits ^{ind} N(0,\sigma^2)\\
\beta_0,\beta_x \mathop \to \limits ^{ind} N(0,\sigma_\beta^2),\quad \sigma \mathop \to \limits Half-Cauchy(A)
\end{array}$$ {#eq:model2}

@@

$$\begin{array}{1}
y_i|x_i,\beta_0,\beta_x,u_1,\cdots,u_k \mathop \to \limits ^{ind} Poisson(exp(\beta_0+\beta_xx_i+\sum_{k=1}^Ku_kz_k(x_i))),\\
x_i \mathop \to \limits ^{ind} Uniform(0,1),\quad u_k|\sigma^2 \mathop \to \limits^{ind} N(0,\sigma^2),\\
\beta_0,\beta_x \mathop \to \limits ^{ind} N(0,10^{10}),\quad \sigma \to Half-Cauchy(10^5)
\end{array}$$ {#eq:model5}

@@

$$\begin{array}{1}
y_i|x_{1i},x_{2i},\beta_0,\beta_{x1},\beta_{x2,u_1,\cdots,u_K} \mathop \to \limits^{ind} Bernoulli(logit^{-1}(\beta_0+\beta_{x1}x_{1i}+\beta_{x2}x_{2i}+\sum_{k=1}^Ku_kz_k(x_{2i}))) \\
x_{1i}\mathop \to \limits ^{ind} Bernoulli(\frac{1}{2}),\quad x_{2i}\mathop \to \limits ^{ind} Uniform(0,1),\\
u_k|\sigma^2 \mathop \to \limits ^{ind} N(0,\sigma^2),\quad \beta_0,\beta_{x1},\beta_{x2} \mathop \to \limits^{ind}N(0,10^{10}),\quad \sigma \to Half-Cauchy(10^5)
\end{array}$$ {#eq:model8}

@@

$$\begin{array}{1}
y_{ij}|x_{1ij},x_{2ij},\beta_0,\beta_{x1},u_11,\cdots,u_{1K_1},u_{21},\cdots,u_{2K_2}\mathop \to \limits^{ind}\\
Poisson(exp(\beta_o+U_i+\beta_{x1}x_{1i}+\sum_{k=1}^{k_1}u_{1k}z_{1k}(x_{1ij})+\beta_{x2}x_{2ij}+\sum_{k=1}^{K_2}u_{2k}z_{2k}(x_{2ij}))) \\
x_{1ij} \mathop \to \limits ^{ind} Uniform(0,1),\quad x_{2ij}\mathop \to \limits^{ind}Uniform(0,1),\\
U_i\mathop \to \limits^{ind} N(0,\sigma^2),\quad u_{1k}|\sigma_{x_1}^2\mathop \to \limits^{ind} N(0,\sigma_{x_1}^2),\quad u_{2k}|\sigma_{x2}^2\mathop \to \limits^{ind} N(0,\sigma_{x_2}^2),\\
\beta_0,beta_{x1},\beta_{x2}\mathop \to \limits^{ind} N(0,10^{10}),\quad \sigma\to Half-Cauchy(10^5),\\
\sigma_{x1}\to Half-Cauchy(10^5),\quad \sigma_{x_2}\to Half-Cauchy(10^5)
\end{array}$$  {#eq:model10}

@@

$$\begin{array}{1}
onycholysis_{ij}|\beta_{terb},\beta_{months},\beta_{terbXmonths},U_i\mathop \to \limits^{ind} Bernoulli(logit^{-1}(\beta_0+U_i+\beta_{terb}(terb_i)+ \\
\beta_{months}(months_{ij})+\beta_{terbXmonths}(terb_i\times months_{ij}))),\quad U_i \mathop \to \limits^{ind}N(0,\sigma^2)
\end{array}$$ {#eq:model12}

>>>>

$$\begin{array}{l}
y_{ij}|x_{ij},\beta_0,\beta_x,U_i,\mathop \to \limits ^{ind} Bernoulli(logit^{-1}(\beta_0+\beta_xx_{ij}+U_i)),\quad 1\leq i \leq m,1\leq j \leq n \\
x_{ij}\mathop \to \limits ^{ind}Uniform(0,1),\quad U_i|\sigma^2 \mathop \to \limits ^{ind} N(0,\sigma^2)\\
\beta_0,\beta_x \mathop \to \limits ^{ind} N(0,\sigma_\beta^2),\quad \sigma \mathop \to \limits Half-Cauchy(A)
\end{array}$$ {#eq:model2}

@@

$$\begin{array}{l}
y_i|x_i,\beta_0,\beta_x,u_1,\cdots,u_k \mathop \to \limits ^{ind} Poisson(exp(\beta_0+\beta_xx_i+\sum_{k=1}^Ku_kz_k(x_i))),\\
x_i \mathop \to \limits ^{ind} Uniform(0,1),\quad u_k|\sigma^2 \mathop \to \limits^{ind} N(0,\sigma^2),\\
\beta_0,\beta_x \mathop \to \limits ^{ind} N(0,10^{10}),\quad \sigma \to Half-Cauchy(10^5)
\end{array}$$ {#eq:model5}

@@

$$\begin{array}{l}
y_i|x_{1i},x_{2i},\beta_0,\beta_{x1},\beta_{x2,u_1,\cdots,u_K} \mathop \to \limits^{ind} Bernoulli(logit^{-1}(\beta_0+\beta_{x1}x_{1i}+\beta_{x2}x_{2i}+\sum_{k=1}^Ku_kz_k(x_{2i}))) \\
x_{1i}\mathop \to \limits ^{ind} Bernoulli(\frac{1}{2}),\quad x_{2i}\mathop \to \limits ^{ind} Uniform(0,1),\\
u_k|\sigma^2 \mathop \to \limits ^{ind} N(0,\sigma^2),\quad \beta_0,\beta_{x1},\beta_{x2} \mathop \to \limits^{ind}N(0,10^{10}),\quad \sigma \to Half-Cauchy(10^5)
\end{array}$$ {#eq:model8}

@@

$$\begin{array}{l}
y_{ij}|x_{1ij},x_{2ij},\beta_0,\beta_{x1},u_11,\cdots,u_{1K_1},u_{21},\cdots,u_{2K_2}\mathop \to \limits^{ind}\\
Poisson(exp(\beta_o+U_i+\beta_{x1}x_{1i}+\sum_{k=1}^{k_1}u_{1k}z_{1k}(x_{1ij})+\beta_{x2}x_{2ij}+\sum_{k=1}^{K_2}u_{2k}z_{2k}(x_{2ij}))) \\
x_{1ij} \mathop \to \limits ^{ind} Uniform(0,1),\quad x_{2ij}\mathop \to \limits^{ind}Uniform(0,1),\\
U_i\mathop \to \limits^{ind} N(0,\sigma^2),\quad u_{1k}|\sigma_{x_1}^2\mathop \to \limits^{ind} N(0,\sigma_{x_1}^2),\quad u_{2k}|\sigma_{x2}^2\mathop \to \limits^{ind} N(0,\sigma_{x_2}^2),\\
\beta_0,beta_{x1},\beta_{x2}\mathop \to \limits^{ind} N(0,10^{10}),\quad \sigma\to Half-Cauchy(10^5),\\
\sigma_{x1}\to Half-Cauchy(10^5),\quad \sigma_{x_2}\to Half-Cauchy(10^5)
\end{array}$$  {#eq:model10}

@@

$$\begin{array}{l}
onycholysis_{ij}|\beta_{terb},\beta_{months},\beta_{terbXmonths},U_i\mathop \to \limits^{ind} Bernoulli(logit^{-1}(\beta_0+U_i+\beta_{terb}(terb_i)+ \\
\beta_{months}(months_{ij})+\beta_{terbXmonths}(terb_i\times months_{ij}))),\quad U_i \mathop \to \limits^{ind}N(0,\sigma^2)
\end{array}$$ {#eq:model12}
